LAGOS lake depth

### 2020-11-25 manuscript/si_template_2019.tex
fight with table S2 bolding

% source at tables/01_predictors.Rmd
\begin{table}
\caption{Summary of lake characteristics for the present study (and for lakes in the contiguous United States). Predictor variables for computing random forest offsets (Equation 2) are printed in bold face. Dashes (-) indicate an identical sample size among this study and that of the contiguous United States.} \label{tableS1}
\centering
\setlength\tabcolsep{1.5pt} % default value: 6pt

\begin{tabular}{lllll}
\hline
Variable & Median & Q25 & Q75 & n\\
\hline
\textbf{Area (ha)} & 55 (33) & 21 (11) & 140 (100) & 4820 (17700)\\
\textbf{Island area (ha)} & 0 (0) & 0 (0) & 0.18 (0.076) & 4820 (17700)\\
- & 1500 (1100) & 880 (640) & 2500 (2200) & 4820 (17700)\\
- & 91 (88) & 41 (40) & 140 (140) & 4820 (17700)\\
- & 710 (560) & 430 (320) & 1200 (1000) & 4820 (17700)\\
- & 380 (290) & 230 (170) & 610 (500) & 4820 (17700)\\
- & 0 (0) & 0 (0) & 58 (25) & 4820 (17700)\\
- & 0 (0) & 0 (0) & 3 (3) & 4820 (17700)\\
- & 0 (0) & 0 (0) & 1 (1) & 4820 (17700)\\
- & 26000 (27000) & 23000 (23000) & 27000 (38000) & 4820 (17700)\\
\textbf{Deepest point distance (m)} & 180 (-) & 110 (-) & 290 (-) & 4820 (-)\\
\textbf{Visual center distance (m)} & 240 (-) & 160 (-) & 390 (-) & 4820 (-)\\
- & 0.046 (-) & 0.024 (-) & 0.079 (-) & 4820 (-)\\

- & 0.062 (-) & 0.029 (-) & 0.14 (-) & 4800 (-)\\

- & 0.077 (-) & 0.051 (-) & 0.11 (-) & 4820 (-)\\

- & 0.077 (-) & 0.038 (-) & 0.13 (-) & 4590 (-)\\

- & 0.077 (-) & 0.037 (-) & 0.13 (-) & 4540 (-)\\
\hline
\end{tabular}
\end{table}

>>>>

% source at tables/01_predictors.Rmd
\begin{table}
\caption{Summary of lake characteristics for the present study (and for lakes in the contiguous United States). Predictor variables for computing random forest offsets (Equation 2) are printed in bold face. Dashes (-) indicate an identical sample size among this study and that of the contiguous United States.} \label{tableS1}
\centering
\setlength\tabcolsep{1.5pt} % default value: 6pt
\begin{tabular}{lllll}
\hline
Variable & Median & Q25 & Q75 & n\\
\hline
Max depth (m) & 8.2 (7) & 4.6 (3.7) & 14 (12) & 4820 (17700)\\
\textbf{Area (ha)} & 55 (33) & 21 (11) & 140 (100) & 4820 (17700)\\
\textbf{Island area (ha)} & 0 (0) & 0 (0) & 0.18 (0.076) & 4820 (17700)\\
\textbf{Perimeter (m)} & 4400 (3500) & 2500 (1800) & 8100 (7300) & 4820 (17700)\\
\textbf{Shoreline development} & 1.7 (1.7) & 1.4 (1.4) & 2.1 (2.2) & 4820 (17700)\\
\textbf{Elevation (m)} & 300 (340) & 180 (210) & 400 (460) & 4820 (17700)\\
\textbf{Watershed-lake ratio} & 7.8 (10) & 3.8 (4.4) & 17 (29) & 4820 (17700)\\
\textbf{Deepest point distance (m)} & 180 (-) & 110 (-) & 290 (-) & 4820 (-)\\
Mean deepest point distance (m) & 140 (-) & 87 (-) & 230 (-) & 4820 (-)\\
\textbf{Visual center distance (m)} & 240 (-) & 160 (-) & 390 (-) & 4820 (-)\\
Inlake slope (m/m) & 0.046 (-) & 0.024 (-) & 0.079 (-) & 4820 (-)\\
Inlake slope online (m/m) & 0.062 (-) & 0.029 (-) & 0.14 (-) & 4800 (-)\\
Inlake slopes (m/m) & 0.057 (-) & 0.032 (-) & 0.098 (-) & 4820 (-)\\
Inlake slopes online (m/m) & 0.07 (-) & 0.034 (-) & 0.15 (-) & 4800 (-)\\
Mean inlake slope (m/m) & 0.043 (-) & 0.021 (-) & 0.09 (-) & 4820 (-)\\
Nearshore mean slope (m/m) & 0.077 (-) & 0.051 (-) & 0.11 (-) & 4820 (-)\\
Nearshore slope online (m/m) & 0.077 (-) & 0.038 (-) & 0.13 (-) & 4590 (-)\\
Nearshore slopes online (m/m) & 0.077 (-) & 0.037 (-) & 0.13 (-) & 4540 (-)\\
\hline
\end{tabular}
\end{table}

### 2020-11-25 tables/01_predictors.Rmd
fight with table S2 bolding

dt <- dt_combined %>%
  dplyr::filter(variable %in% c(slope_distance_vars, 
                           "lake_maxdepth_m", "lake_elevation_m",
                           "lake_perimeter_m", "lake_shorelinedevfactor",
                           "ws_lake_arearatio"))
dt$variable
                       # %>%
  # mutate(n = dt_bathy$n[which(dt_bathy$variable == "inlake_slope")])

@@

dt[9:16,] <- dplyr::arrange(dt[9:16,], variable)

@@

@@

# bold Eq 2 predictor variables
dt_md <- dt
dt_md$Variable[!stringr::str_detect(dt_md$Variable, "slope|Distance|depth") & !is.na(dt_md$Variable)] <- 
  paste0("**", 
         dt_md$Variable[!stringr::str_detect(dt_md$Variable, "slope|Distance|depth") & !is.na(dt_md$Variable)],
         "**")

@@

# bold Eq 2 predictor variables
dt$Variable[!stringr::str_detect(dt$Variable, "slope|Distance|depth") & !is.na(dt_md$Variable)] <- 
  paste0("\\textbf{", 
         dt$Variable[!stringr::str_detect(dt$Variable, "slope|Distance|depth") & !is.na(dt_md$Variable)],
         "}")

# clipr::write_clip(
#   gsub("%\\*\\*", "\\\\%\\*\\*",
#   gsub("_", "\\\\_",
#   gsub("%\\\\", "\\\\%\\\\",
#   sub("\\\\midrule", "\\\\hline",
#   sub("\\\\bottomrule", "\\\\hline",
#   sub("\\\\toprule", "\\\\hline",
#       knitr::kable(dt, digits = 2, format = "latex",
#      booktabs = TRUE, linesep = "", align = c("l"), escape = FALSE)))))))
#    )
```

>>>>

dt <- dt_combined %>%
  dplyr::filter(variable %in% c(slope_distance_vars, 
                           "lake_maxdepth_m", "lake_elevation_m",
                           "lake_perimeter_m", "lake_shorelinedevfactor",
                           "ws_lake_arearatio", "lake_islandarea_ha", 
                           "lake_waterarea_ha"))
# dt$variable
                       # %>%
  # mutate(n = dt_bathy$n[which(dt_bathy$variable == "inlake_slope")])

@@

@@

dt[11:18,] <- dplyr::arrange(dt[11:18,], variable)

@@

model_predictors <- data.frame(
  variable = names(read.csv("../data/depth_predictors.csv", 
                            stringsAsFactors = FALSE)), 
  stringsAsFactors = FALSE) %>%
  dplyr::filter(variable != "lake_maxdepth_m") %>%
  left_join(taxonomy, by = c("variable" = "col_name")) %>%
  pull(pretty) %>% na.omit() %>% as.character()

# bold Eq 2 predictor variables
dt_md <- dt
dt_md$Variable[
  dt_md$Variable %in% model_predictors & !is.na(dt_md$Variable)] <- 
  paste0("**", 
dt_md$Variable[
  dt_md$Variable %in% model_predictors & !is.na(dt_md$Variable)],
         "**")

@@

# bold Eq 2 predictor variables
dt$Variable[
  dt$Variable %in% model_predictors & !is.na(dt$Variable)] <- 
  paste0("\\textbf{", 
dt$Variable[
  dt$Variable %in% model_predictors & !is.na(dt$Variable)],
         "}")

if(interactive()){
  clipr::write_clip(
    gsub("%\\*\\*", "\\\\%\\*\\*",
    gsub("_", "\\\\_",
    gsub("%\\\\", "\\\\%\\\\",
    sub("\\\\midrule", "\\\\hline",
    sub("\\\\bottomrule", "\\\\hline",
    sub("\\\\toprule", "\\\\hline",
        knitr::kable(dt, digits = 2, format = "latex",
       booktabs = TRUE, linesep = "", align = c("l"), escape = FALSE)))))))
     )
}
```
